Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-21 robdml.tex
tex

%

@@

\[
	\big(1-\text{Clip}_0^{U_L}[l_{t-1}]/U_L \big)\times
	U_H
\]

\begin{equation}
	%
	g_\mathsf{B}(H(\cdots);\xi) = H(\cdots) + \xi \cdot (1-\bar{\ell}_{t-1})
	%
\end{equation}

>>>>

% hardness boosting

Such deficiency in the late training process can be alleviated with a
pseudo-hardness function that boosts the destination hardness when the loss
value is low.
%
Denoting the loss value from the previous training iteration as $\ell_{t-1}$,
we first normalize it into $[0,1]$ as $\bar{\ell}_{t-1}=\min(u,\ell_{t-1})/u$,
where $u$ is a manually specified parameter.
%
Note, $u$ is much less than the theoretical upperbound of the loss function,
in order to avoid excessive hardness boost.
%
Then the expectation of destination hardness can be linearly shifted (boosted)
by a scaled constant by a ``hardness boosting'' pseudo-hardness
function, \ie,
%
\begin{equation}
	%
	g_\mathsf{B}(H_\mathsf{D};\xi) = H_\mathsf{D} + \xi \cdot (1-\bar{\ell}_{t-1}).
	%
\end{equation}
%
And the adversarial examples from $\text{HM}(H_\mathsf{S},g_\mathsf{B}(H_\mathsf{D}))$
can be used for training.

@@
